Homework Report

### 2017-02-07 work/work.tex
Starting 3sat to 3color example

To show how this reduction can be done, I'll create an example 3-SAT problem and reduce it to 3-Colorability. Let's take the following 3-SAT expression:

\begin{align*}
\left( x_1 \vee \neg x_2 \vee \neg x_3 \right) \wedge \left( \neg x_1 \vee x_2 \vee x_3 \right) \wedge \left( x_1 \vee x_2 \vee x_3 \right)
\end{align*}

>>>>

To show how this reduction can be done, I'll create an example 3-SAT problem and reduce it to 3-Colorability. This reduction will create a graph \(G = (V, E)\) having \((2n + 3m + 1)\) vertices and \((3n+6m)\) edges \cite{moret}. The process for creating the graph, described below, was taken from \cite{sharma}.\newline

Let's take the following 3-SAT expression:

\begin{align*}
E = \left( x_1 \vee \neg x_2 \vee \neg x_3 \right) \wedge \left( \neg x_1 \vee x_2 \vee x_3 \right) \wedge \left( x_1 \vee x_2 \vee x_3 \right)
\end{align*}

\subsubsection*{Creating the graph}
\begin{enumerate}
\item Create a \emph{triangle} for each variable, i.e. \(x_i\). Each has a common vertex \(B\), called the base vertex. This base vertex will be colored a color, say \(p_1\), so that the other two vertices correspond to the variable and it's negation. 
\item Create a \emph{triangle} for each clause in the formula. 
\item Connect each vertex of a clause triangle to the corresponding literal vertex.
\end{enumerate}

Following the above steps, we generate the following graph \(G\) from our 3-SAT expression \(E\):
